---
title: "Useful R packages"
author: "Stefano Meschiari"
date: "June 16, 2015"
output: 
  md_document:
    variant: markdown_github
---
# My list of useful R packages
Run this Rmarkdown file to download all packages.

* Download packages from GitHub
```{r, eval=FALSE}
install.packages('devtools')
```
* ggplot2 for powerful plotting, themes, and extra functions for arranging 
```{r, eval=FALSE}
install.packages('ggplot2')
install.packages('ggthemes')
install.packages('ggExtra')
devtools::install_github('ggthemr', 'cttobin')
```
* Themes for ggplots
```{r, eval=FALSE}
install.packages('ggextra')
```
* Bit operations
```{r, eval=FALSE}
install.packages('bitops')
```
* Misc plots and data manipulation functions
```{r, eval=FALSE}
install.packages('gdata')
install.packages('gplots')
```
* Functions to work on angular values
```{r, eval=FALSE}
install.packages('circular')
```
* Many misc functions for plots with base graphics
```{r, eval=FALSE}
install.packages('Hmisc')
```
* Enables piping among functions using the ```%>%``` operator
```{r, eval=FALSE}
install.packages('magrittr')
```
* Sane & consistent string handling
```{r, eval=FALSE}
install.packages('stringr')
```
* Generate HTML & LaTeX tables from R objects
```{r, eval=FALSE}
install.packages('xtable')
```
* Operations on R objects and data frames
```{r, eval=FALSE}
install.packages('plyr')
```
* Read CSV and text files faster
```{r, eval=FALSE}
install.packages('readr')
```
* Use additional fonts
```{r, eval=FALSE}
install.packages('showtext')
```
* Integration with plotly and bokeh
```{r, eval=FALSE}
install.packages('plotly')
install.packages('rbokeh')
```
* Three-dimensional OpenGL plots
```{r, eval=FALSE}
install.packages('rgl')
```
* Parallel loops
```{r, eval=FALSE}
install.packages('foreach')
```
* Integrate C++ code in R
```{r, eval=FALSE}
install.packages('Rcpp')
```
* Solve differential equations numerically
```{r, eval=FALSE}
install.packages('deSolve')
```
* SCEPtER pipeline for estimating the stellar age, mass, and radius given observational effective temperature, [Fe/H], and astroseismic parameters. 
```{r, eval=FALSE}
install.packages('ScEptER')
```
* JSON support
```{r, eval=FALSE}
install.packages('jsonlite')
```
* Web scraping
```{r, eval=FALSE}
devtools::install_github("hadley/rvest")
```

